Combinatorics of the geometry of Wilson loop diagrams

### 2019-03-22 General WLD combinatorics.tex
dimension proof

Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ which supports no propagators.  Let $V$ be $W$ with vertex $i$ removed.  Then the Le diagram of $W$ is obtained from the Le diagram of $V$ by inserting an extra column containing all $0$s in position $i$ (i.e. such that the new column has the label $i$).
\end{lem}

@@

\begin{lem}\label{lem dihedral}
If two Wilson loop diagrams differ by a dihedral transformation then their Le diagrams have same number of plusses.
\end{lem}
\begin{proof}
By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments (see \cite[Figure 17.1]{Postnikov} and preceding discussion) of the decorated permutation $\pi_W$ of the positroid associated to $W$.

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that there is a propagator $p$ of $W'$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ with no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
  \end{itemize}
\end{lem}

\begin{proof}
  Remove all vertices of $W$ which do not support any propagators to get a weakly admissible Wilson loop diagram $V$.  Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.  Figure~\ref{fig 3 cases} shows the possible cases, and the reader can easily check that in each case $p$ must be in one of the two situations described above.

  By Lemma~\ref{lem dihedral} there is a dihedral transformation of $V$ which yields a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2. Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
\end{proof}

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of \hlfix{weakly}{check} admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

@@

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

The two possible situations are illustrated in Figure~\ref{fig special p}. The arguments proceed in a similar manner to Lemma~\ref{vertex cyclic int lem}.

We first consider $I_1^{W}$. Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only unassigned propagator when we reach vertex $n-3$ and we have $ I_1^{W}(p) = n-3$.

Next consider $I_n^{W}$, i.e. the set obtained when we apply the Grassmann necklace algorithm with starting vertex $n$. In both cases we have $I_n^{W}(p) = n$. We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$. Therefore the algorithm continues as in $I_1^{V}$, i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

@@

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then the algorithm in $W$ assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occurs in $I_{n-2}^{V}$ so we cannot use the same argument as above. We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$. By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$ (see Figure~\ref{fig special p}); thus $q$ was the final propagator to be assigned in $I_n^{V}$. Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$; this completes all cases for $I_{n-2}^{W}$.

@@

\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Recall that $I_1$ determines the shape of the Le diagram. By Lemma~\ref{lem I} we know that $n,n-1,n-2, n-3 \not\in I_1^{V}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
\end{proof}

@@

Note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.

%Recall Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace. As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position.

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace. In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.

% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{V}$.  Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.  That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.
\end{proof}

@@

\begin{proof}
If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.  Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.  This gives the statement of the lemma.

@@

\begin{lem}\label{lem other k}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then also $n-1\in I_{n-2}^{V}$. Fix a $k$ in the range $1<k<n-2$. Then $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column then this plus is shifted one square left into the $n-2$ column, and no plus was already in that location in the Le diagram of $W$.
\end{lem}

@@

  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.  In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.  By the previous paragraph no other path from $I_k^V$ could end at $n-2$, so since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$.

@@

  Now consider Wilson loop diagrams with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.  Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.  Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p} relative to $W$.

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ relate; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, \ref{lem n-2 bad}, and \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection can be described as follows.
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
  Note that this map is reversible and hence bijective. Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points. However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e. the first bullet point does not apply.

@@

  By Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad}, the bottom row of the diagram of $W$ always contains 3 new plusses; thus $W$ admits $3k + 3$ plusses in total. Applying induction completes the proof.

>>>>

Let $W$ be an admissible Wilson loop diagram with $k$ propagators, and with a vertex $i$ that supports no propagators.  Let $V$ be $W$ with vertex $i$ removed.  Then the Le diagram of $W$ is obtained from the Le diagram of $V$ by inserting an extra column containing all $0$s in position $i$ (i.e. such that the new column has the label $i$).
\end{lem}

@@

\begin{lem}\label{lem dihedral}
If two Wilson loop diagrams differ by a dihedral transformation then their Le diagrams have same number of plusses.
\end{lem}
\begin{proof}
By \cite[Proposition 17.10]{Postnikov}, the dimension of a positroid (and hence the number of plusses in its Le diagram) is $k(n-k) - A(\pi_W)$, where $A(\pi_W)$ denotes the number of alignments of the decorated permutation $\pi_W$ of the positroid associated to $W$. (See \cite[Figure 17.1]{Postnikov} and preceding discussion.)

@@

\begin{lem}\label{lem good p}
  Let $W$ be an admissible Wilson loop diagram with $n\geq 1$ propagators.  Then there is some dihedral transformation $W'$ of $W$ such that $W'$ has a propagator $p$ with the following properties.
  \begin{itemize}
  \item $p = (i, n-1)$ for some $i$, and $p$ has no propagators inside it (that is $i+2, \ldots, n-2$ do not support any propagators in $W'$).
  \item Either the edge $i$ in $W'$ only supports $p$ or the edge $i$ in $W'$ supports exactly one other propagator $q = (j, i)$ with no other propagators inside $q$.
  \end{itemize}
\end{lem}

\begin{proof}
  Remove all vertices of $W$ which do not support any propagators to get a weakly admissible Wilson loop diagram $V$.  Lemma~\ref{lem sian} applied to $V$ gives a length 2 propagator $p$ in $V$ for which either no other propagator is supported on one of the supporting edges of $p$ or there is a second length 2 propagator which is the only other propagator supported on one of the supporting edges of $p$.  (Figure~\ref{fig 3 cases} shows the possible configurations arising from Lemma~\ref{lem sian}, and the reader can easily check that in each case $p$ must be in one of the two situations described above.)

  We can now make a dihedral transformation of $V$ to obtain a diagram satisfying the statement of the lemma with $p$ and $q$ both length 2. Restoring the vertices which do not support any propagators, we obtain a dihedral transformation $W'$ of $W$ as desired (with potentially longer lengths for $p$ and $q$).
\end{proof}

Combining Lemmas \ref{lem uncovered}, \ref{lem dihedral}, and \ref{lem good p}, it therefore suffices to study the Le diagrams of weakly admissible Wilson loop diagrams admitting one of the configurations described in Lemma~\ref{lem good p} with propagators $p$ and $q$ (if $q$ exists) both of length 2. See Figure~\ref{fig special p} for an illustration of the two possibilities.

@@

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} - \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

The two possible cases for $W$ are illustrated in Figure~\ref{fig special p}; all references to the ``left hand case'' or ``right hand case'' below refer to the diagrams in this figure.

We first consider $I_1^{W}$, i.e. the set obtained by applying the Grassmann necklace algorithm to $W$ with starting vertex 1. Note that $n-3 \not\in I_1^{V}$: for the right hand case this is clear from the diagram (since Algorithm~\ref{alg:put GN on WLD} would assign $q$ no later than vertex $n-4$), while for the left hand case it follows from Lemma \ref{lem no fourth vertex}. Therefore when we start at vertex 1 and apply the Grassmann necklace algorithm to $W$, $p$ is the only remaining unassigned propagator when we reach vertex $n-3$, and so we have $ I_1^{W}(p) = n-3$ and $I_1^W = I_1^V\cup \{n-3\}$.

Next consider $I_n^{W}$. From the figure we see that in both cases we have $I_n^{W}(p) = n$. We are now at vertex 1, and the unassigned propagators are exactly those that appear in $V$. Therefore the algorithm continues as in $I_1^{V}$, i.e. we have $I_n^{W} = I_1^{V} \cup \{n\}$. By a similar argument, we must have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$.

@@

Finally, if $n-2,n-1 \in I_{n-2}^{V}$ then in $W$ the algorithm assigns $q$ to $n-2$ and $p$ to $n-1$ as above, but this is different to what occured in $I_{n-2}^{V}$ so we cannot use the same argument as above. We are now at vertex $n$ and only propagators $p$ and $q$ have been assigned; thus we are proceeding as in the construction of $I_n^{V}$ but without propagator $q$. By Lemma~\ref{vertex cyclic int lem} we know that $q$ was assigned to $n-5$ by $I_n^{V}$, and from the diagram we see that the only way this could occur is if all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator to be assigned in $I_n^{V}$. Therefore $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\note{When doing the final formatting, try to ensure that Figure \ref{fig Le} and Lemma \ref{lem shape} are on the same page}
\begin{lem}\label{lem shape}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}.
  The shape of the Le diagram of $V$ can be built from left to right of the following blocks: a rectangle which is 3 columns wide, one more column of the same height, and a partition shape with at most as many rows as the rectangle.
  The shape of the Le diagram of $W$ can be built from left to right of the following blocks: a rectangle with 3 columns and one more row than the first rectangle of $V$, and the same partition shape as in $V$.
\end{lem}

@@

Recall that $I_1$ determines the shape of the Le diagram. By Lemma~\ref{lem I} we know that ${n,n-1,n-2, n-3 \not\in I_1^{V}}$ (which yields the leftmost four columns of the diagram for $V$) and that $I_1^{W} = I_1^{V}\cup \{n-3\}$. This implies that the right hand boundary of the shape of $V$ is the same as the right hand boundary of the shape of $W$ except that $W$ has one additional row of 3 boxes while $V$ has an additional column in the $n-3$ position; that is, an extra column fourth from the left.
\end{proof}

@@

We do this by applying Algorithm~\ref{alg:GN to Le}, which constructs the Le diagram associated to a Grassmann necklace, to the Grassmann necklaces of $V$ and $W$. As described in Section [ref], if Algorithm~\ref{alg:GN to Le} places a $+$ in the box with row index $i$ and column index $j$, we say that this plus is in the $i \rightarrow j$ position, and refer to it as the plus defined by ``the (hook) path from $i$ to $j$''. Note that the collection of paths contributed by a single Grassmann necklace term  must be non-crossing.

Finally, we also note that when we speak of a plus in the Le diagram of $V$ being the same as in $W$ or vice versa, we mean that the position of the plus in $\mathcal{A}$ or $\mathcal{B}$ is the same; because of the column insertion the absolute indices may differ.

@@

Also by Lemma~\ref{lem I} we have $I_{n-1}^{W} = I_n^{V} \cup \{n-1\}$. Recall from the proof of Lemma~\ref{lem I} that $n-3,n-2,n-1,n \not\in I_1^V$; therefore $I_1^W\setminus I_{n-1}^W = (I_1^V \setminus I_n^V) \cup\{n-3\}$, and $n-3$ is maximal in this set. Similarly, 
\[I_{n-1}^W \setminus I_1^W = (I_n^V \setminus I_1^V) \cup \{n-1\} \subseteq \{n-1,n\},\]
where the final inclusion follows from the definition of Grassmann necklace. In particular, $n-1$ is minimal in this set, so Algorithm~\ref{alg:GN to Le} yields a plus in the $(n-3) \rightarrow (n-1)$ position (i.e. the second box in the bottom row of the Le diagram of $W$) along with any plusses yielded by $I_n^V$.
\end{proof}

% Additionally $n-3\not\in I_{n}^{V}$ since if it were then $n-3$ would also be in $I_1^{V}$ and hence propagator $p$ could not contribute $n-3$ to $I_1^{W}$ in contradiction to Lemma~\ref{vertex cyclic int lem}.  Similarly $n-1, n-2\not\in I_n^{V}$.  Thus the paths putting the plusses in from $I_n^{V}$ lie completely in $\mathcal{B}$ or take some vertical boundary edge $>n-3$ to $n$.   Now view these paths in the Le diagram of $W$ and note that the path $n-3\rightarrow n-1$ is compatible, and so these paths together build the plusses that $I_{n-1}^{W}$ contributes.  That is, we get all the plusses from $I_{n}^{V}$ along with a $n-3\rightarrow n-1$ plus, that is a plus in the second to the right box of the bottom row.

@@

\begin{proof}
If $n-2\not\in I_{n-2}^{V}$ then $I_{n-1}^{V}=I_{n-2}^{V}$ by definition, and by Lemma~\ref{lem I} we have $I_{n-2}^{W} = I_{n-1}^{V} \cup \{n-2\}$.  Note that $n-3\not\in I_{n-2}^{V}$ by Lemma~\ref{lem no fourth vertex}.  Therefore the paths controlling the plusses contributed by $I_{n-2}^{W}$ are exactly the paths for $I_{n-1}^{V}$ along with the $(n-3)\rightarrow (n-2)$ path.  This gives the statement of the lemma.
\end{proof}

@@

\begin{lem}\label{lem other k}
  Let $V$ and $W$ be as in Lemma~\ref{lem I}, and suppose that if $n-2\in I_{n-2}^{V}$ then $n-1\in I_{n-2}^{V}$ also. Then for each $k$ in the range $1<k<n-2$, $I_k^{W}$ contributes the same plusses as $I_{k}^{V}$, except that if $I_{k}^{V}$ contributed a plus in the $n-3$ column of the Le diagram of $V$ then this plus is shifted one square left in the Le diagram of $W$, and no plus was already in that location in the Le diagram of $W$.
\end{lem}

@@

  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path from some vertical edge $i$ to the bottom edge $n-3$ in the Le diagram of $V$.  In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.  By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$. All other paths are unchanged.

@@

  Now consider Wilson loop diagrams with $k>1$ propagators.  By Lemma~\ref{lem uncovered} it suffices to prove the result for weakly admissible Wilson loop diagrams with $k$ propagators and no non-supporting vertices.  By Lemma~\ref{lem dihedral} it suffices to prove the result for at least one Wilson loop diagram from each dihedral orbit.  Take a weakly admissible Wilson loop diagram $W$ with $k$ propagators and no non-supporting vertices.  Make a dihedral transformation of $W$ if necessary so that $W$ has a propagator $p$ with the properties in Lemma~\ref{lem good p}.

@@

  From Lemma~\ref{lem shape} we know how the shapes of the Le diagrams of $V$ and $W$ are related; let $\mathcal{A}$ and $\mathcal{B}$ be as described after that lemma.  Lemmas~\ref{lem n and n-1}, \ref{lem n-2 good}, and \ref{lem n-2 bad} tell us that the three boxes of the bottom row of the Le diagram of $W$ each have a plus.  Lemmas~\ref{lem n and n-1} through \ref{lem other k} show that there is a bijection between the plusses of the Le diagram of $V$ and the plusses of the Le diagram of $W$ that are not in the bottom row.  This bijection can be described as follows:
  \begin{itemize}
  \item All plusses from $\mathcal{B}$ for $V$ maintain their positions in $\mathcal{B}$ for $W$.
  \item All plusses from the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ maintain their positions in $\mathcal{A}$ for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus.  This plus is mapped to the $(n-5)\rightarrow (n-1)$ plus for $W$.
  \item All plusses in the $n-3$ column for $V$ are shifted one square to the left in $\mathcal{A}$ for $W$, i.e. into the $n-2$ column.
  \end{itemize}
  Note that this map is reversible and hence bijective. Indeed, the only possible ambiguity is at the $(n-5)\rightarrow (n-1)$ plus in $W$ (if it exists), which could have come from either of the first or third bullet points. However, if the third bullet point applies then by Lemma~\ref{lem n-2 bad} there is no $(n-5)\rightarrow (n-1)$ plus in $V$, i.e. the first bullet point does not apply.

@@

Therefore the Le diagram of $W$ contains $3(k-1)$ plusses in bijection with the plusses from the Le diagram of $V$ and 3 new plusses in the bottom row, yielding $3k$ in total. Applying induction completes the proof.
\end{proof}
